---
title: "Red Wine Quality Analysis"
author: "Erica Racine"
date: "1/4/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

========================================================

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}

library(ggplot2)
library(gridExtra)
library(magrittr)
library(dplyr)
library(scales)


```

```{r echo=FALSE, message=FALSE, warning=FALSE, Load_the_Data}

# Load the Data
setwd("/Users/ericajracine/Documents/Udacity/DAND/5EDA/5EDAProject")
wine <- read.csv('red_wine.csv', header=TRUE, sep=",")

```
This report examines a dataset relating to red variants of a Portugese wine. 
Although I'm a big fan of red wine, I know very little about what constitutes
a high quality wine, and I'm eager to learn more.

# Univariate Plots Section


## Summary Statistics

```{r echo=FALSE, message=FALSE, warning=FALSE, Univariate_Plots_1}

names(wine)

str(wine)

summary(wine)

```
This dataset consists of about 1600 observations and 11+ variables.

```{r echo=FALSE, message=FALSE, warning=FALSE, Univariate_Plots_2}

ggplot(aes(x = quality), data = wine) +
  geom_histogram(binwidth = 1) +
  scale_x_continuous(breaks = 1:10)
```


After looking at the summary data and this first histogram of the distribution
of quality, one of the first things that I saw is that the majority of wines 
fall in the the middle of the quality scale. What chemical chararacteristics 
do wines share on the higher end of the scale (7 or 8)?

Next I wanted to get a bit more familiar with the other variables. I did some 
research to learn a little more about some of the chemical properties listed 
so that I wauld know what I was looking at. I divided the variables into 
smaller groups, though I don't mean to imply any specific correlations between 
the the variables in the same groupings.

Acids


```{r echo=FALSE, message=FALSE, warning=FALSE, Univariate_Plots_3}

fixed.acid.plot1 <- ggplot(aes(x = fixed.acidity), data = wine) +
  geom_histogram()

volatile.acidity.plot1 <- ggplot(aes(x = volatile.acidity), data = wine) +
  geom_histogram()

citric.acid.plot1 <- ggplot(aes(x = citric.acid), data = wine) +
  geom_histogram()

grid.arrange(fixed.acid.plot1, volatile.acidity.plot1, citric.acid.plot1, 
             ncol=3)

```

Then I adjusted the plots a little to zoom in on the data.

```{r echo=FALSE, message=FALSE, warning=FALSE, Univariate_Plots_3b}

fixed.acid.plot2 <- ggplot(aes(x = fixed.acidity), data = wine) +
  geom_histogram(binwidth = .5) +
  scale_x_continuous(limits = c(5, 13), breaks = seq(5, 13, 1))

volatile.acidity.plot2 <- ggplot(aes(x = volatile.acidity), data = wine) +
  geom_histogram(binwidth = .1) +
  scale_x_continuous(limits = c(0, 1.3), breaks = seq(0, 1.3, .1))

citric.acid.plot2 <- ggplot(aes(x = citric.acid), data = wine) +
  geom_histogram(binwidth = .05) +
  scale_x_continuous(limits = c(0, .8))

grid.arrange(fixed.acid.plot2, volatile.acidity.plot2, citric.acid.plot2)

```

Next I looked at residual sugar and chlorides:


```{r echo=FALSE, message=FALSE, warning=FALSE, Univariate_Plots_4}
residual.sugar.plot1 <- ggplot(aes(x = residual.sugar ), data = wine) +
  geom_histogram()

chlorides.plot1 <- ggplot(aes(x =  chlorides), data = wine) +
  geom_histogram()

grid.arrange(residual.sugar.plot1, chlorides.plot1)

```

Two very long tails here!

Let's zoom in.

```{r echo=FALSE, message=FALSE, warning=FALSE, Univariate_Plots_5}

residual.sugar.plot2 <- ggplot(aes(x = residual.sugar ), data = wine) +
  geom_histogram(binwidth = .2)  +
  scale_x_continuous(limits = c(1, 6), breaks = seq(1, 6, 1))

chlorides.plot2 <- ggplot(aes(x =  chlorides), data = wine) +
  geom_histogram()  +
  scale_x_continuous(limits = c(0, .2), breaks = seq(0, .2, .02))

grid.arrange(residual.sugar.plot2, chlorides.plot2)

```

When reading up on the significance of residual sugar in wine, I learned that 
the amount of residual sugar determines how "dry" or "sweet" a wine is 
considered to be. Based on levels I found on a chart online that characterizes 
wines based on their residual sugar levels, I created a new variable, 
"sweetness", which displays whether a wine is characterized as "Dry", 
"Off Dry", "Medium Dry", "Medium Sweet", "Sweet" or "Luscious". Surprisingly, 
the vast majority of the wines in the dataset are "Dry"" wines (95%), and the 
rest are "Off Dry". There were no other catagories represented under 
sweetness.

```{r echo=FALSE, message=FALSE, warning=FALSE, Univariate_Plots_6}

res.sugar <- c(0, 5, 20, 60, 125, 175, Inf)

ratings <- c("Dry", "Off Dry", "Medium Dry", "Medium Sweet", "Sweet", 
             "Luscious")

wine.sweet <- wine %>% mutate(sweetness = cut(residual.sugar, res.sugar, 
                                              labels = ratings))

wine.sweet %>%
                group_by(sweetness) %>%
                summarise(n = n()) %>%
  arrange(sweetness)

wine.sweet.plot1 <- ggplot(aes(x = residual.sugar), data = wine.sweet) +
  geom_histogram() +
  facet_wrap(~sweetness)

wine.sweet.plot1

```

After reading about the controversial wine additives, sulfites, (and the 
contaminants, sulfates) I was curious to see the levels in this sample. Here's 
a look at sulfites/sulfates:

```{r echo=FALSE, message=FALSE, warning=FALSE, Univariate_Plots_7}

free.sulfur.plot1 <- ggplot(aes(x = free.sulfur.dioxide), data = wine) +
  geom_histogram()

total.sulfur.plot1 <- ggplot(aes(x = total.sulfur.dioxide), data = wine) +
  geom_histogram()

sulfates.plot1 <- ggplot(aes(x = sulphates), data = wine) +
  geom_histogram()

grid.arrange(free.sulfur.plot1, total.sulfur.plot1, sulfates.plot1)

```

Let's zoom in...

```{r echo=FALSE, message=FALSE, warning=FALSE, Univariate_Plots_8}

free.sulfur.plot2 <- ggplot(aes(x =  free.sulfur.dioxide), data = wine) +
  geom_histogram(binwidth = 2)  +
  scale_x_continuous(limits = c(0, 40), breaks = seq(0, 40, 2))

total.sulfur.plot2 <- ggplot(aes(x =  total.sulfur.dioxide), data = wine) +
  geom_histogram(binwidth = 5)  +
  scale_x_continuous(limits = c(0, 150), breaks = seq(0, 150, 10))

sulfates.plot2 <- ggplot(aes(x = sulphates ), data = wine) +
  geom_histogram()  +
  scale_x_continuous(limits = c(.3, 1.4), breaks = seq(.3, 1.4, .1))

grid.arrange(free.sulfur.plot2, total.sulfur.plot2, sulfates.plot2)

```

General Properties

Accoding to Wine Spectator, the ideal pH levels for red wine are between 3.3 
to 3.6. I am also interested in seeing if their is any correlation between 
quality and density or alcohol content. Here is quick look at these 
properties...

```{r echo=FALSE, message=FALSE, warning=FALSE, Univariate_Plots_9}

density.plot1 <- ggplot(aes(x =  density), data = wine) +
  geom_histogram()

pH.plot1 <- ggplot(aes(x =  pH), data = wine) +
  geom_histogram()

alchohol.plot1 <- ggplot(aes(x = alcohol), data = wine) +
  geom_histogram()

grid.arrange(density.plot1, pH.plot1, alchohol.plot1)

```


# Univariate Analysis

### What is the structure of your dataset?

There are 1599 observations in this dataset. We will be looking at 12 
variables, all numeric, except for 'quality', which is an integer.

### What is/are the main feature(s) of interest in your dataset?

The main features of interest for me in this dataset are the acids, the 
residual sugar and level of sweetness, sulfites and pH, density and alcohol 
percentage. I'm curious about how and if these variables influence quality.

### What other features in the dataset do you think will help support your \
investigation into your feature(s) of interest?


Including the quality variable in the analysis with other variables will be 
illuminating, and I'm also hoping to discover if the degree of sweetness has 
any effect on the perceived quality of the wine.


### Did you create any new variables from existing variables in the dataset?

I created a "sweetness" variable based on the levels of residual sugar.

### Of the features you investigated, were there any unusual distributions? \
Did you perform any operations on the data to tidy, adjust, or change the form \
of the data? If so, why did you do this?

Other than creating a variable for sweetness, I did not perform any operations 
to tidy, adjust, or change the form of the data.

## Bivariate Plots Section


I'm interested in seeing if any of the variables seem to effect the quality 
variable. I'm also curious to see if sweetness has any correlation with 
quality.

First let's look at the acid variables...

```{r echo=FALSE, message=FALSE, warning=FALSE, Bivariate_Plots_2}

# Summary of wine quality & fixed acidity

wine.quality.fa <- wine %>%
     group_by(quality) %>%
     summarise(fixed_acid_mean = mean(fixed.acidity),
     	fixed_acid_median = median(fixed.acidity),
     	n = n()) %>%
     arrange(quality)
head(wine.quality.fa)

# Boxplot of quality & fixed acidity

fixed.acid.plot3 <-  ggplot(aes(x = factor(quality), y = fixed.acidity), 
                            data = wine) +
 	geom_boxplot()

fixed.acid.plot3

cor.test(wine$fixed.acidity, wine$quality, method = 'pearson')

```

The correlation between quality and fixed acidity appears weak 

```{r echo=FALSE, message=FALSE, warning=FALSE, Bivariate_Plots_3}

# Summary of wine quality & volatile acidity

wine.quality.va <- wine %>%
     group_by(quality) %>%
     summarise(volatile_acid_mean = mean(volatile.acidity),
     	volatile_acid_median = median(volatile.acidity),
     	n = n()) %>%
     arrange(quality)
head(wine.quality.va)

# Boxplot of quality & volatile acidity

volatile.acid.plot3 <-  ggplot(aes(x = factor(quality), y = volatile.acidity), 
                               data = wine) +
 	geom_boxplot()

volatile.acid.plot3

cor.test(wine$volatile.acidity, wine$quality, method = 'pearson')

```

There is a moderately negative relationship between quality and volatile 
acidity.

```{r echo=FALSE, message=FALSE, warning=FALSE, Bivariate_Plots_4}

# Summary of wine quality & citric acid

wine.quality.ca <- wine %>%
     group_by(quality) %>%
     summarise(citric_acid_mean = mean(citric.acid),
     	citric_acid_median = median(citric.acid),
     	n = n()) %>%
     arrange(quality)
head(wine.quality.ca)

# Boxplot of quality & citric acid

citric.acid.plot3 <- ggplot(aes(x = factor(quality), y = citric.acid), 
                            data = wine) +
 	geom_boxplot()

citric.acid.plot3

cor.test(wine$citric.acid, wine$quality, method = 'pearson')

```

There is a positive (but relatively weak) relationship between quality and 
citric acid.

```{r echo=FALSE, message=FALSE, warning=FALSE, Bivariate_Plots_5}

# Summary of wine quality & residual sugar

wine.quality.rs <- wine %>%
     group_by(quality) %>%
     summarise(residual_sugar_mean = mean(residual.sugar),
     	residual_sugar_median = median(residual.sugar),
     	n = n()) %>%
     arrange(quality)
head(wine.quality.rs)

# Boxplot of quality & residual sugar

residual.sugar.plot3 <-  ggplot(aes(x = factor(quality), y = residual.sugar), 
                                data = wine) +
 	geom_boxplot()

residual.sugar.plot3

cor.test(wine$residual.sugar, wine$quality, method = 'pearson')

```

There are a lot of outliers in the 5, 6 and 7 quality range, but there is no 
strong correlation between quality and residual sugar.

```{r echo=FALSE, message=FALSE, warning=FALSE, Bivariate_Plots_6}

# Summary of wine quality & chlorides

wine.quality.ch <- wine %>%
     group_by(quality) %>%
     summarise(chlorides_mean = mean(chlorides),
     	chlorides_median = median(chlorides),
     	n = n()) %>%
     arrange(quality)
head(wine.quality.ch)

# Boxplot of quality & chlorides

chlorides.plot3 <-  ggplot(aes(x = factor(quality), y = chlorides), 
                           data = wine) +
 	geom_boxplot()

chlorides.plot3

cor.test(wine$chlorides, wine$quality, method = 'pearson')

```

There are a lot of outliers in the 5 and 6 quality range, but generally there 
is no strong correlation between chlorides and quality.

```{r echo=FALSE, message=FALSE, warning=FALSE, Bivariate_Plots_7}

# Summary of wine quality & free sulfur dioxide

wine.quality.fsd <- wine %>%
     group_by(quality) %>%
     summarise(free_sulfur_mean = mean(free.sulfur.dioxide),
     	free_sulfur_median = median(free.sulfur.dioxide),
     	n = n()) %>%
     arrange(quality)
head(wine.quality.fsd)

# Boxplot of quality & free sulfur dioxide

free.sulfur.dioxide.plot3 <-  ggplot(aes(x = factor(quality), 
                                         y = free.sulfur.dioxide), 
                                     data = wine) +
 	geom_boxplot()

free.sulfur.dioxide.plot3 

cor.test(wine$free.sulfur.dioxide, wine$quality, method = 'pearson')

```

There is is no strong correlaation between free sulfur dioxide and quality.

```{r echo=FALSE, message=FALSE, warning=FALSE, Bivariate_Plots_8}

# Summary of wine quality & total sulfur dioxide

wine.quality.tsd <- wine %>%
     group_by(quality) %>%
     summarise(total_sulfur_mean = mean(total.sulfur.dioxide),
     	total_sulfur_median = median( total.sulfur.dioxide),
     	n = n()) %>%
     arrange(quality)
head(wine.quality.tsd)

# Boxplot of quality & total sulfur dioxide

total.sulfur.dioxide.plot3 <-  ggplot(aes(x = factor(quality), 
                                          y = total.sulfur.dioxide), 
                                      data = wine) +
 	geom_boxplot() 

total.sulfur.dioxide.plot3

cor.test(wine$total.sulfur.dioxide, wine$quality, method = 'pearson')

```

There is no strong correlation between quality and total sulfur dioxide.


```{r echo=FALSE, message=FALSE, warning=FALSE, Bivariate_Plots_9}

# Summary of quality & sulfates

wine.quality.sul <- wine %>%
     group_by(quality) %>%
     summarise(sulphates_mean = mean(sulphates),
     	sulphates_median = median(sulphates),
     	n = n()) %>%
     arrange(quality)
head(wine.quality.sul)

# Boxplot of quality & sulfates

sulphates.plot3 <-  ggplot(aes(x = factor(quality), y = sulphates), 
                           data = wine) +
 	geom_boxplot() 

sulphates.plot3

cor.test(wine$sulphates, wine$quality, method = 'pearson')


```

Sulfate levels in this sample are slightly higher in the quality levels above 
5. There is a correlation (though relatively weak) between sulfates and 
quality.

```{r echo=FALSE, message=FALSE, warning=FALSE, Bivariate_Plots_10}
# Summary of wine quality & density

wine.quality.den <- wine %>%
     group_by(quality) %>%
     summarise(density_mean = mean(density),
     	density_median = median(density),
     	n = n()) %>%
     arrange(quality)
head(wine.quality.den)

# Boxplot of quality & density

density.plot3 <-  ggplot(aes(x = factor(quality), y = density), data = wine) +
 	geom_boxplot() 

density.plot3

cor.test(wine$density, wine$quality, method = 'pearson')

```

There is no strong correlation between density and quality.

```{r echo=FALSE, message=FALSE, warning=FALSE, Bivariate_Plots_11}

# Summary of wine quality & pH

wine.quality.pH <- wine %>%
     group_by(quality) %>%
     summarise(pH_mean = mean(pH),
     	pH_median = median(pH),
     	n = n()) %>%
     arrange(quality)
head(wine.quality.pH)

# Boxplot of quality & pH

pH.plot3 <-  ggplot(aes(x = factor(quality), y = pH), data = wine) +
 	geom_boxplot() 

pH.plot3

cor.test(wine$pH, wine$quality, method = 'pearson')

```

Interestingly, according to Wine Spectator, the best pH for red wines is 
between 3.3 and 3.6, which both the mean and the median are in between for all 
quality levels, other than the two best levels represented in this dataset, 7 
and 8, where the mean and median levels are slightly less than desirable 
range. However there is a very weak correlation between pH and quality 
(-0.058).

```{r echo=FALSE, message=FALSE, warning=FALSE, Bivariate_Plots_12}

# Summary of quality & alchohol

wine.quality.alc <- wine %>%
     group_by(quality) %>%
     summarise(alcohol_mean = mean(alcohol),
     	alcohol_median = median(alcohol),
     	n = n()) %>%
     arrange(quality)
head(wine.quality.alc)

# Boxplot of quality & pH

alcohol.plot3 <-  ggplot(aes(x = factor(quality), y = alcohol), data = wine) +
 	geom_boxplot()

alcohol.plot3

cor.test(wine$alcohol, wine$quality, method = 'pearson')


```

There seems to be a substantial increase in alcohol levels as quality 
increases, and a fairly strong correlation between alcohol and quality.


Examining sweetness

First I plotted the proportion of each quality level in each level of  
sweetness

```{r echo=FALSE, message=FALSE, warning=FALSE, Bivariate_Plots_13}

wine.sweet.plot2 <- ggplot(aes(x = quality, group = sweetness), 
                           data = wine.sweet) +
  geom_histogram(aes(y = ..prop..), stat="count") +
  scale_x_continuous(breaks = seq(3, 8, 1)) +
  scale_y_continuous(labels=percent) +
  facet_wrap(~sweetness)

wine.sweet.plot2 

```

But it was difficult for me to tell whether 'dry' or 'off dry' wines were of 
better quality. So I ran a summary of the mean and median quality levels of 
both:

```{r echo=FALSE, message=FALSE, warning=FALSE, Bivariate_Plots_13b}

wine.quality.swt <- wine.sweet %>%
     group_by(sweetness) %>%
     summarise(quality_mean = mean(quality),
     	quality_median = median(quality),
     	n = n()) %>%
     arrange(sweetness)
head(wine.quality.swt)
  
```

Clearly both 'dry' and 'off dry' wines are very close in average quality, so 
I know sweetness level is not important to level of quality in this dataset. 
This shouldn't be too surprising after seeing how low the correlation 
coeffecient is between quality and residual sugar.

Alcohol and density

I was reminded while doing a little research on wine components that alcohol 
is less dense than water. So, I wanted to plot alcohol and density, expecting 
to see density decrease as alcohol level increased.

```{r echo=FALSE, message=FALSE, warning=FALSE, Bivariate_Plots_14}

dens.alc.plot1 <-  ggplot(aes(x = alcohol, y = density), data = wine) +
 	geom_point(alpha = 1/2, position = position_jitter(h = 0))

dens.alc.plot1

cor.test(wine$alcohol, wine$density, method = 'pearson')

```

Sure enough, as alcohol level increases, density decreases. There is a fairly 
strong correlation between alcohol and density (.496).


# Bivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. How did the feature(s) of interest vary with other features in \
the dataset?

My main points of note in this investigation were: there is a moderate 
negative relationship between quality and volatile acidity. There is a 
relatively weak positive relationship between quality and citric acid. There 
is a relatively weak positive relationship between quality and sulphates. The 
best pH for red wines is between 3.3 and 3.6, which both the mean and the 
median are in between for all quality levels other than the two best levels 
represented in this dataset, 7 and 8, where the mean and median levels are 
slightly less than desirable range. However there is a very weak correlation 
between pH and quality (-0.058). There seems to be a substantial increase in 
alcohol levels as quality increases, and a fairly strong correlation between 
alcohol and quality. As alcohol level increases, density decreases. There is a 
fairly strong correlation between alcohol and density.

### Did you observe any interesting relationships between the other features \
(not the main feature(s) of interest)?

I was hoping to find an interesting correlation between sweetness and quality, 
but found none. I also examined alcohol and density, and found a fairly strong relationship between the two.

### What was the strongest relationship you found?

The strongest relationships I found were between alcohol and density (with a 
correlation coefficent of .496) and alcohol and quality (with a correlation 
coefficent of .476).

# Multivariate Plots Section

Now that I've found which variables have the more positive relationship with 
quality (alchohol, sulphates and citric acid) , I'm interestd in seeing how 
those variables relate to each other, and their combined effect on quality.

Alcohol, Citric Acid  and Quality

```{r echo=FALSE, message=FALSE, warning=FALSE, Multivariate_Plots_2}

alc.cit.qual.plot1 <-  ggplot(aes(x = alcohol, y = citric.acid, 
                                  color = factor(quality)), data = wine) +
 	geom_point(position = position_jitter(h = 0)) +
  scale_color_brewer(palette = "Blues")

alc.cit.qual.plot1

cor.test(wine$alcohol, wine$citric.acid, method = 'pearson')
```

This plot shows that there are many instances of higher quality wines that 
have higher citric acid or alcohol, independent of the other variable. The 
correlation between alcohol and citric acid proves to be weak (correlation 
coefficient is .110).

Sulphates, Citric Acid and Quality

```{r echo=FALSE, message=FALSE, warning=FALSE, Multivariate_Plots_3}

sul.cit.qual.plot1 <-  ggplot(aes(x = sulphates, y = citric.acid, 
                                  color = factor(quality)), data = wine) +
 	geom_point(alpha = 1/2, position = position_jitter(h = 0)) +
  scale_color_brewer(palette = "Greens")

sul.cit.qual.plot1

cor.test(wine$sulphates, wine$citric.acid, method = 'pearson')

```

It seems as if there are many higher quality wines that are high in both 
citric acid and sulphates. Interestingly, there is a moderately positive 
relationship betweeen citric acid and sulphates (correlation coefficient .313) 

```{r echo=FALSE, message=FALSE, warning=FALSE, Multivariate_Plots_4}

alc.sul.qual.plot1 <-  ggplot(aes(x = alcohol, y = sulphates, 
                                  color = factor(quality)), data = wine) +
 	geom_point(alpha = 1/2, position = position_jitter(h = 0)) +
  scale_color_brewer(palette = "Spectral")

alc.sul.qual.plot1

cor.test(wine$alcohol, wine$sulphates, method = 'pearson')

```

It seems as if the higher quality wines are fairly spread out in this plot. 
There is a weak correlation between alcohol and sulphates (correlation 
coefficient is .094).

# Multivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. Were there features that strengthened each other in terms of \
looking at your feature(s) of interest?

The two variables that I examined here that had the strongest relationship 
were citric acid and sulphates, while the weakest were sulfates and alcohol.

### Were there any interesting or surprising interactions between features? 

Although higher quality wines tend to have higher levels of alchohol and citric 
acid, there is a weaker relationship between alcohol and citric acid than I 
was expecting.

------

### Final Plots and Summary

### Plot One
```{r echo=FALSE, message=FALSE, warning=FALSE, Plot_One}

alcohol.plot3 <-  ggplot(aes(x = factor(quality), y = alcohol), data = wine) +
 	geom_boxplot() +
  ggtitle("Boxplot of Alcohol Percentage and Quality Levels") +
  xlab("Quality Level") + 
  ylab("Alcohol (% by volume)") 

alcohol.plot3

```

### Description One

# This boxplot illustrates the relationship between alcohol and quality. I chose 
# it because these two variables had the strongest correlation of the initial 
# variables I looked at. 


### Plot Two
```{r echo=FALSE, message=FALSE, warning=FALSE, Plot_Two}

wine.sweet.plot2 <- ggplot(aes(x = quality, group = sweetness), 
                           data = wine.sweet) +
  geom_histogram(aes(y = ..prop..), stat="count") +
  scale_x_continuous(breaks = seq(3, 8, 1)) +
  scale_y_continuous(labels=percent) +
  facet_wrap(~sweetness) +
  ggtitle("Histogram of Sweetness and Quality Level") +
  xlab("Quality Level") + 
  ylab("% of Total Count by Sweetness Type")

wine.sweet.plot2

### Description Two

```

Although I was hoping to find an interesting relationship between sweetness 
and quality, this plot represents one of the weakest correlations that I 
discovered between two variables.

### Plot Three
```{r echo=FALSE, message=FALSE, warning=FALSE, Plot_Three}

sul.cit.qual.plot1 <-  ggplot(aes(x = sulphates, y = citric.acid, 
                                  color = factor(quality)), data = wine) +
 	geom_point(alpha = 1/2, position = position_jitter(h = 0)) +
  scale_color_brewer(palette = "Greens") +
  ggtitle("Scatterplot of Sulphate and Citric Acid Levels") +
  xlab("Sulphates (potassium sulphate - g / dm3)") + 
  ylab("Citric Acid (g / dm^3)")

sul.cit.qual.plot1

### Description Three

```

I chose this plot because it showed a surprisingly strong correlation 
between sulphates and citric acid. This relationship might warrant further 
investigation.

------

# Reflection


I learned a great deal through the process of completing this project. I was 
interested doing some background research into the chemical components of 
wine, of which I knew very little. It was exciting to learn that based on the 
level of residual sugar in the wines, I could create a new categorical 
variable that labeled the wines according to how dry or sweet the wines were. 
It was disappointing to find out that the vast majority of wines were dry, and 
that the degree of sweetness had no significant correlation to the quality of 
the wine.

However, it was interesting to see that levels of alchohol, citric acid and 
sulphates did have a positive relationship with quality, and to also confirm 
that alchohol and density would have a strong correlation with each other. 
It was surprising to find that sulphates and citric acid had a moderately 
positive correlation.

I enjoyed this project because it showed me how doing EDA can lead to better 
and more informed questions about your dataset-- I found some interesting 
relationships but know I would have to dig deeper in order to draw any 
conclusions. 

In the future, it would be interesting to ammend the dataset to include a 
wider sample and range of variables such as residual sugar levels, as well as 
other  factors such as where the grapes used to make the wine where from, what
yearthe wine was created, etc. I think that would be helpful to make broader 
conclusions about what variables influence quality.


